Chance of a transition

### 2020-05-21 p_transition/p_transition.Rmd
Can make

```{r}
n <- 2
ps <- rep(NA, n)
for (i in seq_len(n))
  protein_sequence <- bbbq::create_random_tmh(n_aas = 30)
  expect_true(pureseqtmr::is_tmh(protein_sequence))
  p <- calc_p_det_tmh_mut(
    protein_sequence = protein_sequence,
    mhc1_haplotype = mhc1_haplotype
  )
  ps[i] <- p
}
ps
```

>>>>

```{r}
n <- 2
ps <- rep(NA, n)
for (i in seq_len(n)) {
  protein_sequence <- bbbq::create_random_tmh(n_aas = 30)
  expect_true(pureseqtmr::is_tmh(protein_sequence))
  p <- calc_p_det_tmh_mut(
    protein_sequence = protein_sequence,
    mhc1_haplotype = mhc1_haplotype
  )
  ps[i] <- p
}
ps
```
